\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{float}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref} 

\usepackage{amsmath}

\title{Body Weight Track}
\author{Xin Yang}
\date{July 11, 2025 - \today}

\begin{document}

\maketitle

\noindent\textit{There is only one heroism in the world: to see the world as it is and to love it.} \\
— Romain Rolland (1866 -- 1944)

\begin{abstract}
People always tend to believe something wishfully and then take it as the way the world really is, and I am the same. For so many years, I believed that after exercise I needed to replenish enough nutrition, believed that eating more meat would not make me fat, and believed that as long as my exercise performance was okay there would be no problem. But none of these were the real truth of the world. What I thought was “enough nutrition” was actually excessive calories, what I thought was “eating more meat” was actually excessive fat intake, and what I thought was “acceptable exercise performance” could actually be much better.

Body shape is the cumulative reflection of training and nutrition over time. I have reached my target weight with a sustained calorie deficit and high activity, but that is only the first step. Next I need to find new balances: a maintenance balance for keeping daily weight steady; a work–health balance that protects focus, recovery, and long hours at the desk; a high-demand balance for especially busy periods when time and stress spike and so on. This is a starting line, not a finish line.

This record is my full tracking during the process of  weight losing. In the section \ref{sec:Tracking} I recorded the daily tracking of weight, in the section \ref{sec:Summary} the monthly summary, in the section \ref{sec:Supplements} all the supplements I used and the reasons, and in the section \ref{sec:QA} some questions I once had and my own answers.
\end{abstract}

\section{Detailed Tracking}
\label{sec:Tracking}
\begin{longtable}{|c|c|c|c|}
\caption{Body Weight Tracking Everyday} \label{tab:weight} \\

\hline
Date & Time & Weight (lbs) & To Target (lbs) \\
\hline
\endfirsthead

\hline
Date & Time & Weight (lbs) & To Target (lbs) \\
\hline
\endhead

\hline
Date & Time & Weight (lbs) & To Target (lbs) \\
\hline
\endfoot

\hline
\multicolumn{4}{|c|}{{End of table}} \\
\hline
\endlastfoot

\hline
\input{tables/202507}
\input{tables/202508}
\input{tables/202509}
\input{tables/202510}
Oct 14 & 05:01 & 189 & 14 \\
Oct 15 & 08:07 & 189 & 14 \\
Oct 16 & 04:45 & 186 & 11 \\
Oct 17 & 21:30 & 202 & 27 \\
Oct 18 & 07:05 & 194.5 & 19.5 \\
Oct 19 & 04:58 & 194 & 19 \\
End & of & Extreme & Diet \\
\hline
\hline
Start & of & Re-feed & Diet \\
Oct 21 & & & \\
Oct 22 & & & \\
Oct 23 & & & \\
Oct 24 & & & \\
Oct 25 & & & \\
Oct 26 & & & \\
Oct 27 & & & \\
Oct 28 & & & \\
Oct 29 & & & \\
\end{longtable}

\begin{itemize}
\item [Oct 29] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 28] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 27] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 26] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 25] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 24] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 23] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 22] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 21] Sleep h, Energy /10; Diet: kcal, g protein; Cardio:  min treadmill ( mph, incl); Strength: .
\item [Oct 20] Sleep 10 h, Energy 10 /10; Diet: 375 + 700 kcal, 160 g protein; Cardio: 60 min treadmill (3.5 mph, 5.8 incl); Strength: .
\item [Oct 19] Sleep 6 h, Energy 5/10; Diet: 5000 kcal Cardio: some basketball. (Celebration the end of Extreme Diet, Drinking and Hot pot).
\item [Oct 18] Sleep 8 h, Energy 10/10; Diet: 3000 kcal. (In Symposium, No Control).
\item [Oct 17] Sleep 9 h, Energy 10/10; Diet: 4000 kcal, (In Symposium, No Control).
\item [Oct 16] Sleep 12 h, Energy 10/10; Diet: 515 + 4000 kcal, ; (In Symposium, No Control).
\item [Oct 15] Sleep 5 h, Energy 4/10; Diet: 0 kcal, 0 g protein; Busy Day, No exercise, No Calories Intake.
\item [Oct 14] Sleep 6 h, Energy 8/10; Diet: 375 + 700 +375 kcal, 150 g protein; Busy Day, No exercise.
\item [Oct 13] Sleep 6 h, Energy 8/10; Diet: 440 + 1600 kcal, 25 + 150 g protein; Rest Day, Poor Sleep.

\input{itemize/202510}
\input{itemize/202509}
\input{itemize/202508}
\input{itemize/202507}
\end{itemize}


\begin{table}[H]
\centering 
\resizebox{\textwidth}{!}{%
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
    \hline
    Week & 17 Shuttle Run & Push‑up & Plank & Single‑leg B & 5km & Bench Press & Leg Press & Dead Lift \\
    \hline
    Jul 20 - Jul 26 & 85" & 16 & 65" & & & 134*3/3 & 306*10/2 & \\
    Jul 27 - Aug 2 & NF & 11 & & & & 134*6/3 & 396*10/4 & 184*5/1 \\
    Aug 3 - Aug 9 & 78" & 19 & 120" & & 51' & 134*6/3 & 396*10/3 & 184*6/4 \\
    Aug 10 - Aug 16 & 77" & 20 & 55" & & 51' & 134*7/4 & 396*10/4 & 184*7/4 \\
    \hline
    Aug 17 - Aug 23 & Rec Closed & Rec Closed & Rec Closed & Rec Closed & Rec Closed & Rec Closed & Rec Closed & Rec Closed \\
    Aug 24 - Aug 30 & & 16 & 30"/4 & & 50' & & 184*4/2 (squat) & 184*4/2 \\
    Aug 31 - Sep 6 & & 12 & 30"/4 & & 50' & 114*7/4 & 200*10/4 & 164*7/4\\
    Sep 7 - Sep 13 & & 15 & 30"/4 & & 50' &  &  & 184*5/5\\
    \hline
    Sep 14 - Sep 20 & & 15 & 45"/3 & & 51' & 114*7/4 & 164*7/4 (squat) & 164*7/4\\
    Sep 21 - Sep 27 & & & 45"/3 & & 51' & & 164*5/2 (squat) & 114*10/4 \\
    Sep 28 - Oct 4 & & 12 & 45"/3 & & 51' & 114*7/4 & 306*10/3 & 164*7/1 \\
    Oct 5 - Oct 11 & & 14 &  & & 51' & 134*5/4 & 164*7/4 (squat) & 224*2/3 \\
    \hline
    Oct 12 - Oct 18 & &  &  & & 50' & 134*5/4 & 306*10/3 & 204*7/2 \\
    Oct 19 - Oct 25 & &  &  & & & & &  \\
    Oct 26 - Nov 1 & &  &  & & & & & \\
    Nov 2 - Nov 8 & &  &  & & & & & \\
    \hline
    % Sunday - Saturday & 17 Run & Push up & Plank & Single-leg B & 5km & Bench & Squat & Dead Lift
    \end{tabular}%
  }
  \caption{Body Performance Tracking weekly.}
  \label{tab:performance}
\end{table}

\input{subsec/01MonthlySummary}
\input{subsec/02Supplement}
\input{subsec/03QA} 

\end{document}
