\section{Supplements summary:} 
\label{sec:Supplements}
Note: Product order reflects my personal priorities — not a scientific ranking — and some items are unsuitable for people with gastric conditions; if you plan to follow this, please do so under a doctor’s guidance.
\begin{enumerate}
    \item Nature Wise Ashwagandha  
    \begin{enumerate}
        \item Why: Stress resilience, sleep quality, and recovery.
        \item Key actives (2 softgels): Ashwagandha 1,000 mg total = KSM-66 extract 600 mg + organic root powder 400 mg; Ginger extract (Gingever) 20 mg.
    \end{enumerate}

    \item Qunol Turmeric
    \begin{enumerate}
        \item Why: General anti-inflammatory/joint support.
        \item Key actives (2 softgels): Turmeric extract 1,500 mg (curcuminoids 1,425 mg), organic ginger 100 mg, black pepper extract 10 mg (to enhance absorption).
    \end{enumerate}

    \item Nature’s Bounty Hair, Skin \& Nails 
    \begin{enumerate}
        \item Why: Comprehensive hair/skin/nail formula.
        \item Key actives (per daily serving of 3 softgels): Biotin 5,000 mcg.
    \end{enumerate}
    
    \item Kirkland Signature CoQ10 
    \begin{enumerate}
        \item Why: Cellular energy and antioxidant support.
        \item Key active: Coenzyme Q10 300 mg per softgel.
    \end{enumerate}
    
    \item Spring Valley Calcium Citrate
    \begin{enumerate}
        \item Why: Bone health.
        \item Key active: Elemental calcium 600 mg per 2 tablets (as calcium citrate).
    \end{enumerate}
    
    \item Nature Made Fish Oil
    \begin{enumerate}
        \item Why: Heart health and triglyceride support.
        \item Key actives (per softgel): Total Omega-3 720 mg = EPA 360 mg, DHA 300 mg, other Omega-3 60 mg.
    \end{enumerate}
    
    \item XTEND The Original 7g BCAA 
    \begin{enumerate}
        \item Why: pre- and post- workout recovery.
        \item Key actives (per serving): 7 g BCAAs in a 2:1:1 ratio (L-Leucine 3.5 g, L-Isoleucine 1.75 g, L-Valine 1.75 g).
    \end{enumerate}
    
    \item Vital Proteins Collagen Peptides
    \begin{enumerate}
        \item Why: Collagen support for joints, tendons, skin, hair, and nails.
        \item Key actives (per 2 scoops / serving): 20 g hydrolyzed collagen peptides (bovine, Types I \& III; provides about 18 g protein).
    \end{enumerate}

    \item Nature Made D$_3$ 2000 IU
    \begin{enumerate}
        \item Why: Medical Suggestion from SHAW.
        \item Key actives (per softgel): 50 mcg Vitamin D$_3$ as (Cholecalciferol).
    \end{enumerate}

    \item Micronutrient add-on 
    \begin{enumerate}
        \item Sodium (Na): 14\% DV, based on 2300 mg DV.
        \item Potassium (K): 4\% DV, based on 4700 mg DV.
        \item Iron (Fe): 17\% DV, based on 18 mg DV. 
        \item Zinc (Zn): 68\% DV, based on 11 mg DV.
    \end{enumerate} 
\end{enumerate}